---
format:
  html:
    embed-resources: true
    toc: false
    page-layout: full
  docx:
    toc: false
params:
  survey_label: "Survey"
  report_author: ""
  analysis_entity: ""
  analysis_type: ""
  base_unit_dimensions: "None"
  sub_unit_dimensions: "None"
  measure_label: ""
  filters_applied: "None"
  table_title: "Analysis table"
  table_csv: ""
  means_plot: ""
  totals_plot: ""
  has_means_plot: true
execute:
  echo: false
  warning: false
  message: false
---

```{=openxml}
<w:p>
  <w:pPr>
    <w:sectPr>
      <w:pgSz w:w="15840" w:h="12240" w:orient="landscape"/>
      <w:pgMar w:top="720" w:right="720" w:bottom="720" w:left="720" w:header="708" w:footer="708" w:gutter="0"/>
    </w:sectPr>
  </w:pPr>
</w:p>
```

```{r}
table_df <- utils::read.csv(params$table_csv, check.names = FALSE)
numeric_cols <- names(table_df)[vapply(table_df, is.numeric, logical(1))]
if (length(numeric_cols) > 0) {
  table_df[numeric_cols] <- lapply(table_df[numeric_cols], function(x) round(x, 2))
}
```

# `r params$survey_label`

## Open Foris Arena results

`r params$report_author`

## Analysis summary

**Entity:** `r params$analysis_entity`  
**Analysis type:** `r params$analysis_type`  
**Base-unit dimensions:** `r params$base_unit_dimensions`  
**Sub-unit dimensions:** `r params$sub_unit_dimensions`  
**Measure selected:** `r params$measure_label`  
**Filters applied:**  
`r gsub("; ", "  \n", params$filters_applied)`

{{< pagebreak >}}

## Figures

```{r}
if (isTRUE(params$has_means_plot) && nzchar(params$means_plot)) {
  knitr::include_graphics(params$means_plot)
}
```

```{r}
knitr::include_graphics(params$totals_plot)
```
:::
:::

{{< pagebreak >}}

::: {.landscape}

## Table

```{r}
knitr::kable(table_df, format = "pipe")
```
:::
